---
title: "Project Week 4"
author: "Sean"
date: "October 16, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
subtitle: 'ShinyApp: Predict Iris Species Using Machine Learning'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# ShinyApp

This is a quick and easy to use web-based tool that can be used to predict iris species based on given paramters.

---

# How does it work

This app uses machine learning on the available iris dataset to identify the iris species.

The iris dataset consists of 150 measurements across 3 species of iris (*Iris setosa*, *Iris versicolor*, and *Iris virginica*).

The available user defiend paramerts:

* Sepal Length
* Sepal Width
* Petal Length
* Petal Width

---

Traits of Iris Data

```{r}
library(ggplot2)

ggplot(iris, aes(x=Petal.Length, y=Petal.Width, colour=Species)) +
    geom_point() +
    ggtitle("Petal Length by Petal Width Across Iris") +
    ylab("Petal Width") +
    xlab("Petal Length")

```

***

You can also embed plots, for example:

```{r}
library(ggplot2)

ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, colour=Species)) +
    geom_point() +
    ggtitle("Sepal Length by Sepal Width Across Iris Dataset") +
    ylab("Sepal Width") +
    xlab("Sepal Length")
```

---

# Summary

The random forest model used by shinyApp was able to get a test performance of 98% using a 75/25 split of the iris dataset. 

Github repository:

shinyApp Location: https://subarunoaria.shinyapps.io/Project_Week_4/
